Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review

### 2020-11-24 manuscript.Rmd
Rewrite theoretical section

abstract: |
  For many, adolescence marks the onset of emotion dysregulation and related mental health problems. It is therefore essential to have a solid grasp of relevant risk factors. Despite an abundance of empirical research, the literature is somewhat fragmented, as the topic has been investigated from different perspectives across subdisciplines. This systematic review uses text mining to map factors related to adolescent emotion dysregulation. A systematic search for publications that addressed emotion regulation in participants between the ages of 10-25 yielded 6305 suitable papers. One analysis focused on author-provided keywords, and a second extracted sequences of adjectives and nouns from the abstracts. Terms were classified with a dictionary describing 105 terms using 434 regular expressions. Terms were coded as putative “Causes”, “Outcomes”, “Protective factors”, or “Indicators” of emotion dysregulation. We reported term/document frequency, and force-directed graphs of term co-occurrence. These results reﬂected constructs commonly featured in theory and narrative reviews, but also identified underrepresented terms. This illustrates how text mining review may complement narrative reviews. Importantly, most constructs were directly related to emotion dysregulation, with few interconnections between constructs – reflecting the fragmented literature. This research constitutes a first step towards integrating the literature, and may inspire future empirical and theoretical work.

keywords          : "emotion regulation, adolescence, systematic review, text mining, machine learning"
wordcount         : "5400"
bibliography      : ["veni_sysrev.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man,noextraspace"
output            : papaja::apa6_pdf
knit              : worcs:::cite_essential
---

@@

<!-- Emotion regulation in adolescence is important -->
A key developmental challenge in adolescence is acquiring mature emotion
regulation skills [@croneUnderstandingAdolescencePeriod2012;
@zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to
mental health[@aldaoEmotionregulationStrategiesPsychopathology2010;
@schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014]
and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
as one in five people, adolescence marks the onset of emotion
regulation-related mental illness, which can persist throughout the life course
[see @leeAdolescentMentalHealth2014]. It is therefore crucial to identify which
risk factors and environmental hazards render some adolescents more susceptible
to emotional difficulties than others. Although there is an abundance of
empirical work on adolescents' emotion regulation, the literature is somewhat
fragmented, as the topic has been investigated from different (sub)disciplines.
This systematic review seeks to overcome this limitation by using
bibliographic analysis to map all factors currently
considered to be relevant to adolescent emotion regulation. <!-- Ergens anders: Similarly, although
there are several *relevant* theories, there is no specific theoretical
framework to guide research on adolescents' emotion regulation. Although theory
development is beyond the scope of this paper, we set out to generate a
proto-theoretical nomological network of the potential risk factors,
manifestations, and outcomes of emotion regulation in adolescence. We discuss
how this nomological network relates to existing relevant theory, and conclude
with recommendations for future theory-generating efforts.-->

## Why adolescence is an important life phase for emotion regulation

Adolescence is defined as a life phase ranging from pubertal onset to
adult-like independence [@steinbergAgeOpportunityLessons2014].
It is thus demarcated by both biological- and socio-cultural factors.
It has been argued that,
due to accellerated pubertal onset and delayed transitions to adult roles,
adolescence now ranges from 10-24 years in the modern Western world
[@sawyerAgeAdolescence2018].

@@

## Existing relevant theory

Theory is of paramount importance when seeking to understand or explain a
phenomenon. Although there are many relevant theories, none have specifically
addressed emotion regulation development in adolescence. Several recent
publications have undertaken the monumental task of comprehensively reviewing
theory relevant to emotional development
[@bussTheoriesEmotionalDevelopment2019;
@riedigerEmotionRegulationAdolescence2014]. Thanks, in part, to these efforts,
we can provide a summary review of the theoretical landscape as context for our
empirical contribution.<!--Several recent publications have undertaken the
monumental task of providing a comprehensive overview of theories of emotional
development [e.g., @bussTheoriesEmotionalDevelopment2019;
@holodynskiDevelopmentEmotionsEmotion2006;
@riedigerEmotionRegulationAdolescence2014], and of the empirical work
pertaining to emotions in adolescence
[@coe-odessEmergentEmotionsAdolescence2019].  -->

Two theories widely invoked to frame research on development, including
emotional development, are Bronfenbrenner's bioecological model, and Sameroff's
transactional model. Bronfenbrenner's model
[@bronfenbrennerBioecologicalModelHuman2007] describes how the environment
shapes individual development. Each individual is imbued with certain
biological predispositions, and develops over time, in interaction with
contextual influences. These influences range from the microsystem, composed of
those people close to the individual, to the macrosystem, consisting of
indirect political and economic influences, to the exosystem, consisting of
cultural norms and values. Sameroff's model is somewhat compatible with the
bioecological model [@sameroffUnifiedTheoryDevelopment2010], but focuses more
on the interplay between nature and nurture. It conceptualizes development as a
product of reciprocal influences between the child and the environment.
Sameroff distinguishes between proximal influences, for instance, through
parents (the microsystem in Bronfenbrenner's model), and distal influences;
structural factors indirectly shaping development, like socio-economic status,
schools, and the community (macro- and exosystem). With increasing age, distal
influences gradually gain ground on proximal influences.

Turning now towards theories specifically addressing emotion regulation in
adolescence, Hall's notion of "storm and stress" is one of the oldest [see
@arnettAdolescentStormStress1999]. It describes how hormonal changes diminish
self-control and increase reactivity, leading to difficulties in emotion
regulation, conflict with parents, and risky behavior. Recent work provides a
more nuanced perspective on this theory. For example, although the notion of
diminished self-control and increased emotional reactivity has been upheld, it
has been recast as a necessary change that facilitates emotional maturation
[@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].
More recently, Sroufe [-@sroufeEmotionalDevelopmentOrganization1995] presented
a theory focused on normative emotional development in early childhood. It
argues that, as children grow older, their increasing self-regulatory abilities
drive a transition from external emotion regulation by primary caregivers
towards autonomous emotion regulation. This theory focuses on two drivers of
development: social and cognitive influences. Social influences mainly occur
through parental co-regulation, parenting behaviors, and parent-child
attachment. Cognitive influences occur through the development of the central
nervous system (CNS), cognition, and self-regulation. Several other theories,
introduced below, have extemporized on these sources of influence.

Several other models echo this emphasis on neorocognitive development as a driver of emotional
development, including emotion regulation development.
For example, polyvagal theory closely links emotional experience
- and regulation - to autonomous nervous system functioning
[@porgesOrientingDefensiveWorld1995]. A more recent neorocognitive theory, with
substantial relevance to adolescents' emotion regulation development, is Crone
and Dahl's model of social-affective engagement and goal flexibility
[@croneUnderstandingAdolescencePeriod2012]. This theory is based on the notion
of a "maturity gap" in middle-adolescence, arising from a developmental
asymmetry between motivational and inhibitory brain circuits
[@craccoEmotionRegulationChildhood2017;
@caseyBrakingAcceleratingAdolescent2011]. To
a greater extent than related writings, however, @croneUnderstandingAdolescencePeriod2012
set out to explain adolescents' diverging destinies; the
question why some youngsters flourish while others languish. Crone and Dahl
argue that adolescents' cognitive engagement is dynamically responsive to
social and motivational goal salience. This flexibility, on the one hand,
prepares adolescents to effectively engage cognitive systems in novel
challenging situations in a way that facilitates developing mature regulatory
abilities. On the other hand, it places them at risk to act impulsively in
pursuit of peer approval. In terms of explanans,
this theory focuses primarily on cognitive factors
and the role of peers, with less attention to factors such as parenting.

A theory focused specifically on parents' role in emotion regulation
development is Morris' tripartite model [-@morrisRoleFamilyContext2007]. It
describes three pathways through which parents shape emotion regulation
development: Through observation and modeling, parenting practices, and the
emotional family climate, which in turn involves attachment and marital
relationship quality. Morris and colleagues also emphasize the relevance of
fathers and siblings, and others have adapted the tripartite model to describe
the role of peers in adolescents' emotion regulation development
[@reindlSocializationEmotionRegulation2016].

Whereas our primary interest is in theories of emotional development,
theories of the phenomenon of
emotion regulation are also somewhat relevant. One influential theory is Gross'
[-@grossHandbookEmotionRegulation2013] process model, which describes the
process of emotion regulation, from eliciting cue to ultimate response.
Individuals modulate the different stages of this process using strategies,
consciously or otherwise. The effectiveness, desireability, and consequences of
different strategies depend on the cultural context [see
@bariolaChildAdolescentEmotion2011]. Similar to Gross' theory, the social
information processing theory of emotion also describe the role of intrapsychic
processes and strategies in emotion experience and reulation
[@lemeriseIntegratedModelEmotion2000].

Another theory worth mentioning in this context is
@holodynskiDevelopmentEmotionsEmotion2006's internalization model of emotional
development. It applies Vygotsky's theory of development to the domain of
emotion, and presents a detailed integrated model of emotional experience and
regulation. Like Sroufe's work, this work describes a transition from
interpersonal to intrapersonal emotion regulation. Other important features of
this work include the interplay between emotion and communication, and the
internalization of the socio-cultural symbolic function of emotion throughout
development. <!--Theories like this are particularly relevant to a fine-grained
understanding of the process of emotion regulation, but their developmental
relevance has unfortunately not yet been considered (REF Buss). -->

@@

Despite the abundance of relevant theory,
the existing literature has several limitations when the goals is to
identify which
risk factors render some adolescents more susceptible
to maladaptive emotional development than others.
One crucial shortcoming
is the lack of explicit attention to the life phase of adolescence. This is
unfortunate, as empirical research consistently indicates that adolescence is a
crucial life phase for emotion regulation development. Adolescence differs
qualitatively from infancy, childhood, and adulthood. It is therefore
questionable whether theories focused on different ages can be generalized to adolescents.
By contrast, some theories focus on adolescence specifically [e.g.,
@croneUnderstandingAdolescencePeriod2012], but only address emotion regulation
in passing.
A second, related, shortcoming is that some relevant theories lack
a developmental component <!--, and thus lack a well-substantiated
understanding of developmental processes--> [see
@bussTheoriesEmotionalDevelopment2019;
@croneUnderstandingAdolescencePeriod2012]. 
A third shortcoming is that theories
vary widely in scope: Some are very broad and all-encompassing, but somewhat
non-specific, such as the biopsychosocial models of Bronfenbrenner and
Sameroff. Others describe a specific phenomenon in great detail, but are not
embedded in a larger unifying framework. Examples include Morris' tripartite
model, Crone and Dahl's model, and polyvagal theory. It would be beneficial to
bridge these levels of analysis.
One limitation echoed across many
publications in this field is that more theory formation is required to provide
a unified framework that could guide future empirical work.
The present study
seeks to lay the groundwork for such theory development,
by providing an inductive conceptual
review of the field.

@@

Several authors of comprehensive reviews have noted that developmental theories
of emotion are still in their infancy [@bussTheoriesEmotionalDevelopment2019].
Several specific limitations of the theoretical landscapes precipitate the
present study. First, although there are many *relevant* theories, few are
focused specifically on emotion regulation. Second, the phase of adolescence is
rarely addressed, although empirical research has indicated that this is a
crucial period of emotion regulation development.
"emotion theory has largely focused on adults, and emotional development theory
has largely focused on infancy and early childhood (see Chap. 24 on adolescent
emotional development)." Buss et al 2019:20

@@

<!-- NIET TEVEEL OVER THEORIE PRATEN; IK KIJK NIET NAAR THEORIE. IK KIJK NAAR FACTOREN DIE IN VERBAND GEBRACHT WORDEN MET EMOTIEREGULATIE. -->
<!--The life phase of adolescence differs qualitatively from both childhood and adulthood. It is therefore not sufficient to extend -->

@@

if(!file.exists("recs_final.csv")){
  recs_final <- unique_recs[screen$key[!screen$drop_these], ]
  write.csv(recs_final, "recs_final.csv", row.names = FALSE)
} else {
  recs_final <- read.csv("recs_final.csv")
}
```
Papers were screened based on two main criteria:
First, papers had to address emotion regulation, emotional problems, or similar.
Second, the target population must overlap with the life phase of adolescence, defined as the age range from 10-25.
Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
Screening was initially conducted in Rayyan QRCI [@Ouzzani2016].
Papers were sorted using Rayyan's ranking algorithm.
To train the algorithm on exclusion criteria, screening focused on abstracts most likely to be excluded.
After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI [@van_de_schoot_rens_2020_3828293].
This program uses text mining and active learning to build a customizable machine learning model for article inclusion.
We used a naive Bayes model, and focused on exclusion of irrelevant papers.
In ASReview, an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers were screened.
Screening again focused on articles most likely to be excluded, and continued until, among the most recently screened 100 papers, only 6 were excluded.
The screening procedure is detailed in Figure \@ref(fig:prismachart).
In total, `r nrow(recs_final)` papers were retained for analysis.

@@

```{r, warning=FALSE, message=FALSE}
source("study1.R")
if(run_everything | !file.exists("Study1_lda_dims.txt")) source("LDA_analysis.R")
lda_dims <- read_yaml("Study1_lda_dims.txt")
```
The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
We extracted keywords by document, and used a dictionary
created specifically for this study to classify related terms.
The dictionary describes `r length(dict)` terms using `r length(unlist(dict))`
regular expression queries.
The lead author composed a first draft of the dictionary.
This draft was subsequently updated in two ways:
First, while writing the introduction for this paper,
key terms from the literature were added to the dictionary.
Second, by including frequently occurring uncategorized words during preliminary analyses of the data until no more frequently occurring uncategorized words were found.
An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.
After applying the dictionary and exclusion filter,
and removing records with no (remaining) keywords,
the resulting corpus consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique words.
<!--As term-document frequency is irrelevant in the context of keywords (i.e., keywords should not occur twice within the same document, except when two synonyms have been recoded using the dictionary),
the term-document matrix was dichotomized.-->

>>>>

abstract: |
  Adolesence is a developmentally sensititve period for emotion dysregulation. Although substantial empirical research has addressed relevant risk factors, an integrating framework is lacking. This systematic review of 6305 papers uses text mining to map correlates of adolescents’ (ages 10-25) emotion dysregulation. One analysis focused on author-provided keywords; a second analysis parsed the abstracts. Terms were coded as putative “Causes”, “Outcomes”, “Protective factors”, or “Indicators”. We reported term/document frequency, and force-directed graphs of term co-occurrence. These results reﬂected constructs commonly featured in theory and narrative reviews, but also identified underrepresented terms. This research constitutes a first step towards integrating the literature, and may inspire future empirical and theoretical work.
It also illustrates how text mining reviews may complement narrative reviews. <!--SH I would end with a more memorable take-home about how text-mining can be useful to researchers (e.g., when topics are of multi-disciplinary interest but each field has their own preferred methods and/or terminology)-->

keywords          : "emotion regulation, adolescence, systematic review, text mining, machine learning"
wordcount         : "5400"
bibliography      : ["veni_sysrev.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man,noextraspace"
output            : papaja::apa6_word
knit              : worcs:::cite_essential
---

@@

<!-- Emotion regulation in adolescence is important -->
A key developmental challenge in adolescence is acquiring mature emotion
regulation skills [@croneUnderstandingAdolescencePeriod2012;
@zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to
mental health [@aldaoEmotionregulationStrategiesPsychopathology2010;
@schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014]
and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
as one in five people, adolescence marks the onset of emotion
regulation-related mental illness, which can persist throughout the life course
[see @leeAdolescentMentalHealth2014]. 
It is therefore crucial to identify which
risk factors and environmental hazards render some adolescents more susceptible
to emotional difficulties than others. <!--SH: Main goal of paper -->
The present review set out to address this question.
Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, as the topic has been investigated from different (sub)disciplines.
This systematic review seeks to overcome this limitation by adopting a novel method -
text mining based bibliographic analysis - to map all factors currently
considered to be relevant to adolescent emotion regulation.
Text mining can reveal important topics in a body of literature,
and reveal which constructs are often studied together.
It is therefore uniquely suited to comprehensively review a prolific but fragmented field,
potentially revealing topics and connections missed by narrative reviewers,
and laying the groundwork for future empirical and theoretical work.
<!-- SH: this implies that the main contribution of the paper is predominantly methodological is that the case? Is there some primary thesis/argument that will be advanced? It is really important to take a top-down approach to that messaging, beginning here in the first paragraph-->
<!-- Ergens anders: Similarly, although
there are several *relevant* theories, there is no specific theoretical
framework to guide research on adolescents' emotion regulation. Although theory
development is beyond the scope of this paper, we set out to generate a
proto-theoretical nomological network of the potential risk factors,
manifestations, and outcomes of emotion regulation in adolescence. We discuss
how this nomological network relates to existing relevant theory, and conclude
with recommendations for future theory-generating efforts.-->

## Why adolescence is an important life stage for emotion regulation

Adolescence is defined as a life stage ranging from pubertal onset to
adult-like independence [@steinbergAgeOpportunityLessons2014].
It is thus demarcated by both biological and socio-cultural factors.
It has been argued that,
due to accellerated pubertal onset and delayed transitions to adult roles,
adolescence now ranges from 10-24 years in the modern Western world
[@sawyerAgeAdolescence2018].

@@

## Existing theoretical landscape

The structure of the empirical literature on adolescents' emotion regulation is best understood against the backdrop of the existing theoretical landscape.
This allows us to see in what respects 
phenomenon.
We therefore provide a summary review of the theoretical landscape as context for our
empirical contribution.
Several recent publications provide more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
It is apparent from these reviews that, although many theories are *relevant* for emotion regulation development in adolescence, few have addressed this topic directly.
Fewer theories still have comprehensively addressed important predictors of development in this life stage,
and none directly guide contemporary research in the field [see @bussTheoriesEmotionalDevelopment2019].
There is thus a need for more integrative theory formation [see @riedigerEmotionRegulationAdolescence2014].

Hall's notion of "storm and stress" is one of the oldest relevant theories of adolescents' emotional development [see
@arnettAdolescentStormStress1999]. It describes how hormonal changes diminish
self-control and increase reactivity, leading to difficulties in emotion
regulation, conflict with parents, and risky behavior.
In modern theories, this notion of diminished self-control and increased emotional reactivity has been - although it is now considered to be a normative change that facilitates emotional maturation
[@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].

<!--SH I am still not sure what the empirical contribution is - can you be more specific with it in this sentence? -->
<!--Several recent publications have undertaken the
monumental task of providing a comprehensive overview of theories of emotional
development [e.g., @bussTheoriesEmotionalDevelopment2019;
@holodynskiDevelopmentEmotionsEmotion2006;
@riedigerEmotionRegulationAdolescence2014], and of the empirical work
pertaining to emotions in adolescence
[@coe-odessEmergentEmotionsAdolescence2019].  -->

Two theories widely invoked to frame research on development, including
emotional development, are Bronfenbrenner's bioecological model, and Sameroff's
transactional model. Bronfenbrenner's model
[@bronfenbrennerBioecologicalModelHuman2007] describes how the environment
shapes individual development. Each individual is imbued with certain
biological predispositions, and develops over time, in interaction with
contextual influences. These influences range from the microsystem, composed of
those people close to the individual, to the macrosystem, consisting of
indirect political and economic influences, to the exosystem, consisting of
cultural norms and values. Sameroff's model is somewhat compatible with the
bioecological model [@sameroffUnifiedTheoryDevelopment2010], but focuses more
on the interplay between nature and nurture. It conceptualizes development as a
product of reciprocal influences between the child and the environment.
Sameroff distinguishes between proximal influences, for instance, through
parents (the microsystem in Bronfenbrenner's model), and distal influences;
structural factors indirectly shaping development, like socio-economic status,
schools, and the community (macro- and exosystem). With increasing age, distal
influences gradually gain ground on proximal influences.
<!--SH I am not sure what contribution this paragraph ultimately makes - you should consider condensing it substantially to just note that these theories have something to say about emotional development but are not adolescent-specific-->

One example of a normative theory of emotional development in early childhood is presented by Sroufe [-@sroufeEmotionalDevelopmentOrganization1995].
Sroufe argues that, as children grow older,
their increasing self-regulatory abilities
drive a transition from external emotion regulation by primary caregivers
towards autonomous emotion regulation. This theory focuses on two drivers of
development: social and cognitive influences. Social influences mainly occur
through parental co-regulation, parenting behaviors, and parent-child
attachment. Cognitive influences occur through the development of the central
nervous system (CNS), cognition, and self-regulation.

This emphasis on social influences and neurocognitive development is reflected in many theories.
Some of these focus primarily on neurocognitive development.
For example, polyvagal theory closely links emotional experience
- and regulation - to autonomous nervous system functioning
[@porgesOrientingDefensiveWorld1995].
A more recent neurocognitive theory, with
substantial relevance to adolescents' emotion regulation development, is Crone
and Dahl's model of social-affective engagement and goal flexibility
[@croneUnderstandingAdolescencePeriod2012]. Like other authors 
[e.g., @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017],
Crone and Dahl argue that the developmental
asymmetry between motivational and inhibitory brain circuits gives rise to a
"maturity gap" in middle adolescence. 
What sets Crone and Dahl apart from related writings, however, 
is the greater attention to adolescents' diverging destinies:
the question why some youngsters flourish while others languish.
They argue that adolescents' cognitive engagement is dynamically responsive to
social and motivational goal salience. This flexibility, on the one hand,
prepares adolescents to effectively engage cognitive systems in novel
challenging situations in a way that facilitates developing mature regulatory
abilities. On the other hand, it places them at risk to act impulsively in
pursuit of peer approval. In terms of explanans,
this theory focuses primarily on cognitive factors
and the role of peers, with less attention to factors such as parenting.

Other theories emphasize socialization to a greater extent.
One such theory is Morris' tripartite model, which focuses specifically on parents' role in emotion regulation development [-@morrisRoleFamilyContext2007].
It describes three pathways through which parents shape emotion regulation
development: Through observation and modeling, parenting practices, and the
emotional family climate, which in turn involves attachment and marital
relationship quality. Morris and colleagues also emphasize the relevance of
fathers and siblings, and others have adapted the tripartite model to describe
the role of peers in adolescents' emotion regulation development
[@reindlSocializationEmotionRegulation2016].
A more abstract take on socialization is found in @holodynskiDevelopmentEmotionsEmotion2006's
internalization model of emotional development. 
Unique aspects emphasized in this theory are the interplay between emotion and communication,
and the internalization of the cultural symbolic function of emotion.
<!--Like Sroufe, Holodynski describes an age graded transition from
interpersonal to intrapersonal emotion regulation.
In doing so, Holodynski applies Vygotsky's theory of development to the domain of
emotion, and presents a detailed integrated model of emotional experience and
regulation.-->

Finally, theories of the phenomenon of emotion regulation offer a unique perspective on potential proximal drivers of emotion regulation development.
One influential theory is Gross'
[-@grossHandbookEmotionRegulation2013] process model, which describes the
process of emotion regulation, from eliciting cue to ultimate response.
According to Gross, individuals use strategies to modulate the different stages of this process,
consciously or otherwise. Culture plays a role too, as the effectiveness, desireability, and consequences of different strategies depend on the social context [see
@bariolaChildAdolescentEmotion2011]. Similar to Gross' theory, the social
information processing theory of emotion also describe the role of cognitive
processes and strategies in emotion experience and regulation
[@lemeriseIntegratedModelEmotion2000].

<!--Theories like this are particularly relevant to a fine-grained
understanding of the process of emotion regulation, but their developmental
relevance has unfortunately not yet been considered (REF Buss). -->

@@

Despite the abundance of relevant theory,
the existing literature has several limitations when the goals is to
identify which
risk factors render some adolescents more susceptible
to maladaptive emotional development than others.
One crucial shortcoming
is the lack of explicit attention to the life stage of adolescence. This is
unfortunate, as empirical research consistently indicates that adolescence is a
crucial life stage for emotion regulation development. Adolescence differs
qualitatively from infancy, childhood, and adulthood. It is therefore
questionable whether theories focused on different ages can be generalized to adolescents.
By contrast, some theories focus on adolescence specifically [e.g.,
@croneUnderstandingAdolescencePeriod2012], but only address emotion regulation
in passing.
A second, related, shortcoming is that some relevant theories lack
a developmental component <!--, and thus lack a well-substantiated
understanding of developmental processes--> [see
@bussTheoriesEmotionalDevelopment2019;
@croneUnderstandingAdolescencePeriod2012]. 
A third shortcoming is that theories
vary widely in scope: Some are very broad and all-encompassing, but somewhat
non-specific, such as the biopsychosocial models of Bronfenbrenner and
Sameroff. Others describe a specific phenomenon in great detail, but are not
embedded in a larger unifying framework. Examples include Morris' tripartite
model, Crone and Dahl's model, and polyvagal theory. It would be beneficial to
bridge these levels of analysis.
One limitation echoed across many
publications in this field is that more theory formation is required to provide
a unified framework that could guide future empirical work.
The present study
seeks to lay the groundwork for such theory development,
by providing an inductive conceptual
review of the field.

@@

Several authors of comprehensive reviews have noted that developmental theories
of emotion are still in their infancy [@bussTheoriesEmotionalDevelopment2019].
Several specific limitations of the theoretical landscapes precipitate the
present study. First, although there are many *relevant* theories, few are
focused specifically on emotion regulation. Second, the stage of adolescence is
rarely addressed, although empirical research has indicated that this is a
crucial period of emotion regulation development.
"emotion theory has largely focused on adults, and emotional development theory
has largely focused on infancy and early childhood (see Chap. 24 on adolescent
emotional development)." Buss et al 2019:20

@@

<!-- NIET TEVEEL OVER THEORIE PRATEN; IK KIJK NIET NAAR THEORIE. IK KIJK NAAR FACTOREN DIE IN VERBAND GEBRACHT WORDEN MET EMOTIEREGULATIE. -->
<!--The life stage of adolescence differs qualitatively from both childhood and adulthood. It is therefore not sufficient to extend -->

@@

if(!file.exists("recs_final.csv")){
  recs_final <- unique_recs[screen$key[!screen$drop_these], ]
  write.csv(recs_final, "recs_final.csv", row.names = FALSE)
} else {
  recs_final <- read.csv("recs_final.csv")
}
```
Papers were screened based on two main criteria:
First, papers had to address emotion regulation, emotional problems, or similar.
Second, the target population must overlap with the life stage of adolescence, defined as the age range from 10-25.
Thus, for example, an article reviewing the role of hormonal changes in emotional adjustment throughout the entire life course, including adolescence, would be deemed relevant.
Screening was initially conducted in Rayyan QRCI [@Ouzzani2016].
Papers were sorted using Rayyan's ranking algorithm.
To train the algorithm on exclusion criteria, screening focused on abstracts most likely to be excluded.
After coding `r sum(screen$rayyan == "True")+sum(screen$rayyan == "False")` papers, screening continued in ASReview - a free, open source alternative to Rayyan QRCI [@van_de_schoot_rens_2020_3828293].
This program uses text mining and active learning to build a customizable machine learning model for article inclusion.
We used a naive Bayes model, and focused on exclusion of irrelevant papers.
In ASReview, an additional `r sum(table(screen$included, screen$rayyan)[, 1])` papers were screened.
Screening again focused on articles most likely to be excluded, and continued until, among the most recently screened 100 papers, only 6 were excluded.
The screening procedure is detailed in Figure \@ref(fig:prismachart).
In total, `r nrow(recs_final)` papers were retained for analysis.

@@

```{r, warning=FALSE, message=FALSE}
source("study1.R")
if(run_everything | !file.exists("Study1_lda_dims.txt")) source("LDA_analysis.R")
lda_dims <- read_yaml("Study1_lda_dims.txt")
dtm_top <- read_yaml("study1_dtm_top.yml")
```
The corpus for this first analysis consisted of the author-provided keywords for the selected articles.
We extracted keywords by document, and used a dictionary
created specifically for this study to classify related terms.
The dictionary describes `r length(dict)` terms using `r length(unlist(dict))`
regular expression queries.
The lead author composed a first draft of the dictionary.
This draft was subsequently updated in two ways:
First, while writing the introduction for this paper,
key terms from the literature were added to the dictionary.
Second, by including frequently occurring uncategorized words during preliminary analyses of the data until no more frequently occurring uncategorized words were found.
An exclusion list of methodological terms and other non-substantive words was generated using the same procedure.
After applying the dictionary and exclusion filter,
and removing records with no (remaining) keywords,
the resulting corpus consisted of `r number_docs_words[1]` documents with `r number_docs_words[2]` unique words.
<!--As term-document frequency is irrelevant in the context of keywords (i.e., keywords should not occur twice within the same document, except when two synonyms have been recoded using the dictionary),
the term-document matrix was dichotomized.-->
